---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```


The `MultiHorizonSPA` package allows R users to run the Multi Horizon Superior Predictive Ability (SPA) test proposed by Quaedvlieg (2021): compare the predictive performance of two distinct models when jointly considering all horizons of a forecast path.

## Installation

You can install `MultiHorizonSPA` from CRAN  as follows:

```{r cran-installation, eval = FALSE}
install.packages("MultiHorizonSPA")
```

or from GitHub:

```{r gh-installation, eval = FALSE}
install.packages("devtools")
devtools::install_github("lucabarbaglia/MultiHorizonSPA")
```


## A start-up example

Test for uniform SPA (uSPA).

```{r test uSPA}
library(MultiHorizonSPA)
data(LossDiff_uSPA)
Test_uSPA(LossDiff=LossDiff_uSPA, L=3)
```

The output of the  `Test_uSPA` function is a list containing two objects:

- p-value: the p-value for uSPA;

- t_uSPA: the statistics for uSPA;


Now test for average SPA (aSPA).

```{r test aSPA}
library(MultiHorizonSPA)
data(LossDiff_aSPA)
weights <- t(as.matrix(rep(1, ncol(LossDiff_aSPA))/ncol(LossDiff_aSPA)))
Test_aSPA(LossDiff=LossDiff_aSPA, weights=weights, L=3)
```

The output of the  `Test_aSPA` function is a list containing two objects:

- p-value: the p-value for aSPA;

- t_aSPA: the statistics for aSPA.


## References:

* Quaedvlieg, Rogier. "Multi-horizon forecast comparison." Journal of Business & Economic Statistics 39.1 (2021): 40-53.



