---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```


The `MultiHorizonSPA` package allows R users to run the Multi Horizon Superior Predictive Ability (SPA) test proposed by Quaedvlieg (2021).

## Installation

You can install `MultiHorizonSPA` from GitHub as follows:

```{r gh-installation, eval = FALSE}
install.packages("devtools")
devtools::install_github("lucabarbaglia/MultiHorizonSPA")
```


## A start-up example

Test for uniform SPA (uSPA).

```{r test uSPA}
library(MultiHorizonSPA)
data(LossDiff_uSPA)
Test_uSPA(LossDiff=LossDiff_uSPA, L=3)
```

The output of the  `Test_uSPA` function is a list containing two objects:

- p-value: the p-value for uSPA;

- t_uSPA: the statistics for uSPA;

The first element of the output list provides the overall average sentiment score of each text, while the second provides the detailed score of each chunk of text that relates to one of the ToI.


Now test for average SPA (aSPA).

```{r test aSPA}
library(MultiHorizonSPA)
data(LossDiff_aSPA)
weights <- matlab::ones(1,20)/20
Test_aSPA(LossDiff=LossDiff_aSPA, weights=weights, L=3)Test_uSPA(LossDiff=LossDiff_uSPA, L=3)
```

The output of the  `Test_aSPA` function is a list containing two objects:

- p-value: the p-value for aSPA;

- t_sSPA: the statistics for aSPA.


## References:

* Quaedvlieg, Rogier. "Multi-horizon forecast comparison." Journal of Business & Economic Statistics 39.1 (2021): 40-53.



